---
title: "rmarkdownpractice2"
author: "Blake Yost"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

Today is `r Sys.Date()`


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(easystats)
library(modelr)
library(broom)
library(kableExtra)
```

Give me a report on mpg, including model selection and coefficient table etc. 
Oh, and at least one pretty plot.

## Pretty plot by cylinder
```{r}
x <- mpg
plot1 <- 
x %>% 
  ggplot(aes(x=displ,y=hwy,color=factor(cyl)))+
  geom_smooth(method = "lm")
plot1
```

## Summary of model 1
```{r}
m1 <- glm(data=x,
    formula = hwy~displ+factor(cyl))
tidym1 <- m1 %>% broom::tidy()
tidym1 %>% 
  kable() %>% 
  kable_classic()
```

## Summary of model 2
```{r}
m2 <- glm(data=x,
          formula = hwy~displ*factor(cyl))
tidym2 <- m2 %>% broom::tidy()
tidym2 %>% 
  kable() %>% 
  kable_classic()
```

## Comparing the perfomance of model 1 and 2
```{r}
compare_performance(m1,m2) %>% plot
```

## Prediction 
A car with displacement 1.8, cylinder 4 based on model 2
```{r}
y <- data.frame(displ = 1.8,
           cyl = 4)
predict(m2,newdata = y)
```

## Adding predictions for the entire dataset
```{r}
preds <- add_predictions(x,m2)
preds %>% 
  select("manufacturer", "model", "displ", "cyl", "hwy" ,"pred")
```

## Plot of predictions
```{r}
plot2 <- 
preds %>% 
  ggplot(aes(x=displ,y=pred,color=factor(cyl)))+
  geom_smooth(method = "lm")
plot2
```

## Adding predicictions onto plot 
Pink line is the predictions
```{r}
plot3 <- plot1 + geom_smooth(data = preds, aes(x = displ, y = pred, color = factor(cyl)), color = "pink")
plot3
```



